Fundamental Problems with the Evidence Base of Adolescent Depression Treatments.

### 2024-02-26 apples_and_oranges.qmd
Meta-analysis for percent women

@@

met_perc_women <- metagen(TE = "percent_women",
                           seTE = "percent_women_std_error",
                           studlab = "new_study_id",
                          data = df_long_for_metan,
                           sm = "SMD",
                           fixed = FALSE,
                           random = TRUE,
                           method.tau = "REML",
                           hakn = TRUE,
                           title = "percentage women across studies",
                          subgroup = "four_level_var",
                          tau.common = FALSE,
                          na.rm = TRUE)

>>>>

# Turn age sd into se

df_long_for_metan <- df_long_for_metan %>% 
  mutate (se_age = sd_age / sqrt(baseline_n) )

@@

df_for_gender_metan <- list_df_simulated[[1]] %>% 
  filter(!is.na(percent_women))

met_perc_women <- metagen(TE = percent_women,
                           seTE = percent_women_std_error,
                           studlab = new_study_id,
                           data = df_for_gender_metan,
                           sm = "SMD",
                           fixed = FALSE,
                           random = TRUE,
                           method.tau = "REML",
                           hakn = TRUE,
                           title = "percentage women across studies",
                           subgroup = four_level_var,
                           tau.common = FALSE)
met_perc_women

# Now start looking at age variable

df_for_age_metan <- list_df_simulated[[1]] %>% 
  filter(!is.na(mean_age))

met_age <- metagen(TE = mean_age,
                           seTE = sd_age / sqrt(baseline_n),
                           studlab = new_study_id,
                           data = df_for_age_metan,
                           sm = "SMD",
                           fixed = FALSE,
                           random = TRUE,
                           method.tau = "REML",
                           hakn = TRUE,
                           title = "age across studies",
                           subgroup = four_level_var,
                           tau.common = FALSE)

met_age
